\documentclass[a4paper,10pt]{article}
\usepackage[left=0.7in, right=0.7in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}

% Formatting
\renewcommand{\baselinestretch}{1.0}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\pagestyle{empty}

% HEADER
\begin{center}
    {\huge \textbf{Marouane Guerouji}} \\[2pt]
    Arlington, VA \quad | \quad (202) 600-5891 \quad | \quad \texttt{ma.guerouji@gmail.com} \\ 
    \texttt{www.linkedin.com/in/m-guerouji} \quad | \quad \texttt{www.mguerouji.com}
\end{center}

\vspace{-3mm}

% PROFESSIONAL SUMMARY
\section*{Professional Summary}
Entry-level \textbf{Software Engineer} with expertise in \textbf{Full Stack Development, Cloud Computing, and Agile Methodologies}. Proficient in \textbf{Java, Python, JavaScript, and AWS}, with experience in designing and deploying \textbf{scalable, high-performance applications}. Certified \textbf{AWS Developer – Associate} and \textbf{AWS Cloud Practitioner}. Strong foundation in \textbf{Object-Oriented Programming (OOP), RESTful APIs, and DevOps}. Passionate about problem-solving and optimizing software efficiency. \textbf{Eligible for Secret Clearance.}

\vspace{-3mm}

% EDUCATION
\section*{Education}
\textbf{B.S. in Computer Science} \hfill \textbf{Dec 2023} \\
George Mason University, Fairfax, VA 

\vspace{-3mm}

% TECHNICAL SKILLS
\section*{Technical Skills}
\textbf{Languages:} Java, Python, JavaScript, C, Go, SQL \\
\textbf{Web:} HTML, CSS, React, Bootstrap, Node.js, Express.js \\
\textbf{Cloud:} AWS (Lambda, EC2, S3, DynamoDB, CloudFormation), Docker, CI/CD \\
\textbf{Databases:} SQL, NoSQL (DynamoDB) \\
\textbf{Tools:} Git, GitHub, GitLab, Jira, Eclipse, JetBrains IDEs \\
\textbf{Testing:} JUnit, Postman \\
\textbf{Concepts:} Agile, Scrum, OOP, RESTful APIs, DevOps 

\vspace{-3mm}

% CERTIFICATIONS
\section*{Certifications}
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item AWS Certified Developer – Associate
    \item AWS Certified Cloud Practitioner
    \item AWS Certified Solutions Architect – Associate
    \item CompTIA Security+ (SY0-701)
\end{itemize}

\vspace{-3mm}

% PROJECTS
\section*{Projects}
\textbf{Dice Game Server} – Java, Spring Boot, JavaScript, Docker
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item Developed a \textbf{Full Stack dice game} with authentication and secure \textbf{JSON data management}.
    \item \textbf{Optimized data retrieval by 50\%} with efficient Object-Oriented Design.
    \item Achieved \textbf{95\% test coverage} using JUnit and Postman.
\end{itemize}

\textbf{Socializing Forum} – Node.js, Express.js, AWS EC2, EJS
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item Built an \textbf{interactive forum} with AWS-hosted backend, supporting \textbf{real-time anonymous posting}.
    \item Ensured \textbf{99.9\% uptime} by leveraging AWS EC2 and optimized database queries.
\end{itemize}

\textbf{Portfolio Website} – HTML, CSS, JavaScript, REST API
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item Designed a \textbf{responsive portfolio site} with \textbf{real-time weather API integration}.
    \item Improved \textbf{page load speed by 40\%} using optimization techniques.
\end{itemize}

\vspace{-3mm}

% EXPERIENCE
\section*{Experience}
\textbf{Rideshare Driver} \hfill Uber \& Lyft | Apr 2016 – Present
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item \textbf{Maintained 5-star rating} by optimizing routes and ensuring excellent service.
    \item Applied \textbf{data-driven decision-making} to maximize ride efficiency.
\end{itemize}

\textbf{Restaurant Manager} \hfill Babalu Lounge | Apr 2014 – Aug 2016
\begin{itemize}[leftmargin=0.3in, itemsep=1pt]
    \item Increased VIP table sales by \textbf{15\%} through targeted promotions.
    \item Managed customer relations, strengthening leadership and communication skills.
\end{itemize}

\vspace{-3mm}

% ADDITIONAL INFORMATION
\section*{Additional Information}
\textbf{U.S. Citizen} \quad | \quad \textbf{Open to relocation} \quad | \quad \textbf{Eligible for Secret Clearance}

\end{document}
